It turns out that neither the master method, nor the Akra-Bazzi method apply here.
The former fails due to the fact that the driving function does not grow polynomially slower than the watershed function, as explained in the book on page 105 for a similar recurrence.
And the latter fails because the integral $\int_1^n\frac{dx}{x\lg x}$ used in equation (4.23) for this recurrence does not converge.

We'll use a different approach for $T(n)$, instead considering a family of recurrences $T_b(n)=bT_b(n/b)+n/\!\lg n$ for a constant $b>1$, where $T(n)$ belongs.
Let's use the change-of-variables method from \refProblem{4-3}, letting $m=\log_bn$.
Then, $n=b^m$, and we obtain
\[
    T_b(b^m) = bT_b(b^{m-1})+\frac{b^m}{m\lg b}.
\]
Defining $S_b(m)=T_b(b^m)$ produces the new recurrence
\[
    S_b(m) = bS_b(m-1)+\frac{b^m}{m\lg b}.
\]

Assume that $T_b(n)=\Theta(1)$ for $n<b$, which means that $S_b(m)=\Theta(1)$ for $m<1$.
We'll show by induction on $m\ge1$ that $S_b(m)=b^m(H_m+\Theta(1))/\lg b$, where $H_m$ is the $m$th harmonic number.
For $m=1$,
\begin{align*}
    S_b(1) &= bS_b(0)+\frac{b}{\lg b} \\[1mm]
    &= b\cdot\Theta(1)+\frac{bH_1}{\lg b} \\[1mm]
    &= \frac{b^1(H_1+\Theta(1))}{\lg b} && \text{(because $\lg b\cdot\Theta(1)=\Theta(1)$)},
\end{align*}
so the base case holds.
For the inductive step, let $m\ge2$, and adopt the inductive hypothesis $S_b(m-1)=b^{m-1}(H_{m-1}+\Theta(1))/\lg b$ to get
\begin{align*}
    S_b(m) &= b\cdot\frac{b^{m-1}(H_{m-1}+\Theta(1))}{\lg b}+\frac{b^m}{m\lg b} \\[1mm]
    &= \frac{b^m(H_{m-1}+\Theta(1))+b^m\!/m}{\lg b} \\[1mm]
    &= \frac{b^m(H_m+\Theta(1))}{\lg b} && \text{(because $\Theta(1)+1/m=\Theta(1)$)} \\[1mm]
    &= \frac{b^m\ln m+\Theta(1)}{\lg b} && \begin{minipage}{2.25in}(by equation (A.9),\\\null\quad and because $b^m\cdot\Theta(1)=\Theta(1)$)\end{minipage} \\[1mm]
    &= \Theta(b^m\lg m).
\end{align*}
Changing back from $S_b(m)$ to $T_b(n)$, we obtain $T_b(n)=T_b(b^m)=S_b(m)=\Theta(b^m\lg m)=\Theta(n\lg\log_b n)=\Theta(n\lg\lg n)$.

As we can see, the asymptotic solution to $T_b(n)$ doesn't depend on $b$, so it also applies to recurrence $T(n)\equiv T_3(n)$ that we study in this part.
